---
title: "Milestone Report"
author: "Daniel Jungen"
date: "20 Februar 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Milestone Report

In this document we will cover some exploratory analysis of the text files that can be found in this link:
https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

First we download them to our working directory
```{r, echo = FALSE}
setwd("D://coursera//Capstone Project")
library(stringi)
```

```{r}
if (!file.exists("Coursera-SwiftKey.zip")) {
  download.file("https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip", "Coursera-SwiftKey.zip")
  unzip("Coursera-SwiftKey.zip")}
```
Since the readers of this document all speak english, we will only focus on the text files with english content.

```{r, warning = FALSE, cache = TRUE}
con <- file("final//en_US//en_US.blogs.txt")
blogs <- readLines(con,encoding = "UTF-8", skipNul = TRUE)
close(con)

con <- file("final//en_US//en_US.twitter.txt")
twitter <- readLines(con,encoding = "UTF-8", skipNul = TRUE)
close(con)

con <- file("final//en_US//en_US.news.txt")
news <- readLines(con,encoding = "UTF-8", skipNul = TRUE)
close(con)
```

In order to get an overview over the structure of the files we briefly show some figures:

```{r, cache = TRUE}
l_blogs<-length(blogs)
l_twitter<-length(twitter)
l_news<-length(news)

n_words_blogs<-sum(stri_count_words(blogs))
n_words_twitter<-sum(stri_count_words(twitter))
n_words_news<-sum(stri_count_words(news))

facts<-data.frame(Medium = c("Blogs", "Twitter", "News"), Lines=c(l_blogs,l_twitter,l_news), Words=c(n_words_blogs,n_words_twitter, n_words_news))

facts

```

