---
title: "Milestone Report"
author: "Daniel Jungen"
date: "14 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Milestone Report

## Loading the data

In this document we will cover some exploratory analysis of the text files that can be found in this link:
https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

First we download them to our working directory
```{r, echo = FALSE}
setwd("D://coursera//Capstone Project")
```
and load the neccessary libraries

```{r, message=FALSE, warning = FALSE}
library(stringi)
library(tm)
library(textreg)
library(tokenizers)
library(RWeka)
```


```{r}
if (!file.exists("Coursera-SwiftKey.zip")) {
  download.file("https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip", "Coursera-SwiftKey.zip")
  unzip("Coursera-SwiftKey.zip")}
```
Since the readers of this document all speak english, we will only focus on the text files with english content.

```{r, warning = FALSE, cache = TRUE}
con <- file("final//en_US//en_US.blogs.txt")
blogs <- readLines(con,encoding = "utf-8", skipNul = TRUE)
close(con)

con <- file("final//en_US//en_US.twitter.txt")
twitter <- readLines(con,encoding = "utf-8", skipNul = TRUE)
close(con)

con <- file("final//en_US//en_US.news.txt")
news <- readLines(con,encoding = "utf-8", skipNul = TRUE)
close(con)
```

## Some analysis of the uncleaned data

In order to get an overview over the structure of the files we briefly show some figures:

```{r, cache = TRUE}
l_blogs<-length(blogs)
l_twitter<-length(twitter)
l_news<-length(news)

n_words_blogs<-sum(stri_count_words(blogs))
n_words_twitter<-sum(stri_count_words(twitter))
n_words_news<-sum(stri_count_words(news))

w_p_l_blogs<-n_words_blogs/l_blogs
w_p_l_twitter<-n_words_twitter/l_twitter
w_p_l_news<-n_words_news/l_news

facts<-data.frame(Medium = c("Blogs", "Twitter", "News"), Lines=c(l_blogs,l_twitter,l_news), Words=c(n_words_blogs,n_words_twitter, n_words_news), AVG = c(w_p_l_blogs, w_p_l_twitter, w_p_l_news))

facts

```

As we can see the average number of words in a tweet is much lower than the number of words in a blog or in some news. This is due to the restriction of characters in twitter. So no big surprise at all.

The next thing to do is

## Cleaning the data

One would expect more cleaning effort when it comes to cleaning tweets. There are at least two obvious reasons:

* Limitation of characters leads to strong use of abbrivations
* As a medium used by many people not just for reading but also for writing there will be a strong use of emoticons such as ";-), :-),..." This might occur in blogs as well but is quite unlikely to appear in the news.

A good but of course not representative example is the following tweet:
```{r, cache = TRUE}
twitter[30]
```
So in order to get an idea of the structure of the text we take a sample of 0.1% (due to memory restrictions) and clean it using the tm_map-function:


```{r, cache=TRUE}

set.seed(4711)
blogs_sample<-sample(blogs, length(blogs)*0.001, replace = FALSE)
news_sample<-sample(news, length(news)*0.001, replace = FALSE)
twitter_sample<-sample(twitter, length(twitter)*0.001, replace = FALSE)

textsample<-c(blogs_sample,news_sample,twitter_sample)

textcorpus<-VCorpus(VectorSource(textsample))


textcorpus <- tm_map(textcorpus, removeNumbers)
textcorpus <- tm_map(textcorpus, removePunctuation)
textcorpus <- tm_map(textcorpus, stripWhitespace)
textcorpus <- tm_map(textcorpus, content_transformer(tolower))
textcorpus <- tm_map(textcorpus, removeWords, stopwords("en"))
textcorpus <- tm_map(textcorpus, PlainTextDocument)

unigramtoken <- function(x) NGramTokenizer(x, Weka_control(min =1, max = 1))
bigramtoken <- function(x) NGramTokenizer(x, Weka_control(min =2, max = 2))
trigramtoken <- function(x) NGramTokenizer(x, Weka_control(min =3, max = 3))


getFreq <- function(tdm) {
  freq <- sort(rowSums(as.matrix(tdm)), decreasing = TRUE)
  return(data.frame(word = names(freq), freq = freq))
}

freq_one_word <- getFreq(removeSparseTerms(TermDocumentMatrix(textcorpus), 0.9999))

freq_two_words <- getFreq(removeSparseTerms(TermDocumentMatrix(textcorpus, control = list(tokenize = bigramtoken)), 0.9999))

freq_three_words <- getFreq(removeSparseTerms(TermDocumentMatrix(textcorpus, control = list(tokenize = trigramtoken)), 0.9999))
```


```{r}
head(freq_one_word)
head(freq_two_words)
head(freq_three_words)
```


